Brownian Dynein Model

### 2015-07-29 latex/derivation.tex
Add Mathematica symbolic matrix equation solution.
Add Mathematica formatted (ish) equations.
Add symbols to numerically solve for angular velocities to derivation.tex.
Hit problem with ftest: cannot evaluate test expressions with manually-set angular velocities. Modifying dynein_struct.cpp to calculate angular velocities.

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{graphicx}

\usepackage{fullpage}

\newtheorem{theorem}{Theorem}

@@

\section{Preparing Equations for Matrix Form}

@@

\section{Make a matrix!}

@@

\begin{align}
  A_1\dot{\Theta}_{bl} + A_2 \dot{\Theta}_{ml} + A_3 \dot{\Theta}_{mr} + A_4 \dot{\Theta}_{br} &= X_1 \\
  B_1\dot{\Theta}_{bl} + B_2 \dot{\Theta}_{ml} + B_3 \dot{\Theta}_{mr} + B_4 \dot{\Theta}_{br} &= X_2 \\
  C_1\dot{\Theta}_{bl} + C_2 \dot{\Theta}_{ml} + C_3 \dot{\Theta}_{mr} + C_4 \dot{\Theta}_{br} &= X_3 \\
  \frac{A_4D_1}{D_4}\dot{\Theta}_{bl} + \frac{A_4D_2}{D_4}\dot{\Theta}_{ml} + \frac{A_4D_3}{D_4}\dot{\Theta}_{mr} + A_4 \dot{\Theta}_{br} &= \frac{A_4}{D_4}X_4 \\
\end{align}

\begin{align}
  \left(A_1 - \frac{A_4D_1}{D_4}\right)\dot{\Theta}_{bl} + \left(A_2 - \frac{A_4D_2}{D_4}\right)\dot{\Theta}_{ml} + \left(A_3 - \frac{A_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= X_1 - \frac{A_4}{D_4}X_4\\
  B_1\dot{\Theta}_{bl} + B_2 \dot{\Theta}_{ml} + B_3 \dot{\Theta}_{mr} + B_4 \dot{\Theta}_{br} &= X_2 \\
  C_1\dot{\Theta}_{bl} + C_2 \dot{\Theta}_{ml} + C_3 \dot{\Theta}_{mr} + C_4 \dot{\Theta}_{br} &= X_3 \\
  \frac{B_4D_1}{D_4}\dot{\Theta}_{bl} + \frac{B_4D_2}{D_4}\dot{\Theta}_{ml} + \frac{B_4D_3}{D_4}\dot{\Theta}_{mr} + B_4 \dot{\Theta}_{br} &= \frac{B_4}{D_4}X_4 \\
\end{align}

\begin{align}
  \left(A_1 - \frac{A_4D_1}{D_4}\right)\dot{\Theta}_{bl} + \left(A_2 - \frac{A_4D_2}{D_4}\right)\dot{\Theta}_{ml} + \left(A_3 - \frac{A_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= X_1 - \frac{A_4}{D_4}X_4\\
  \left(B_1 - \frac{B_4D_1}{D_4}\right)\dot{\Theta}_{bl} + \left(B_2 - \frac{B_4D_2}{D_4}\right)\dot{\Theta}_{ml} + \left(B_3 - \frac{B_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= X_1 - \frac{B_4}{D_4}X_4\\
  C_1\dot{\Theta}_{bl} + C_2 \dot{\Theta}_{ml} + C_3 \dot{\Theta}_{mr} + C_4 \dot{\Theta}_{br} &= X_3 \\
  \frac{C_4D_1}{D_4}\dot{\Theta}_{bl} + \frac{B_4D_2}{C_4}\dot{\Theta}_{ml} + \frac{C_4D_3}{D_4}\dot{\Theta}_{mr} + C_4 \dot{\Theta}_{br} &= \frac{C_4}{D_4}X_4 \\
\end{align}

\begin{align}
  \left(A_1 - \frac{A_4D_1}{D_4}\right)\dot{\Theta}_{bl} + \left(A_2 - \frac{A_4D_2}{D_4}\right)\dot{\Theta}_{ml} + \left(A_3 - \frac{A_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= X_1 - \frac{A_4}{D_4}X_4\\
  \left(B_1 - \frac{B_4D_1}{D_4}\right)\dot{\Theta}_{bl} + \left(B_2 - \frac{B_4D_2}{D_4}\right)\dot{\Theta}_{ml} + \left(B_3 - \frac{B_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= X_1 - \frac{B_4}{D_4}X_4\\
  \left(C_1 - \frac{C_4D_1}{D_4}\right)\dot{\Theta}_{bl} + \left(C_2 - \frac{C_4D_2}{D_4}\right)\dot{\Theta}_{ml} + \left(C_3 - \frac{C_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= X_1 - \frac{C_4}{D_4}X_4\\
  \frac{C_4D_1}{D_4}\dot{\Theta}_{bl} + \frac{B_4D_2}{C_4}\dot{\Theta}_{ml} + \frac{C_4D_3}{D_4}\dot{\Theta}_{mr} + C_4 \dot{\Theta}_{br} &= \frac{C_4}{D_4}X_4 \\
\end{align}

\begin{align}
  \left(A_1 - \frac{A_4D_1}{D_4}\right)\dot{\Theta}_{bl} + \left(A_2 - \frac{A_4D_2}{D_4}\right)\dot{\Theta}_{ml} + \left(A_3 - \frac{A_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= X_1 - \frac{A_4}{D_4}X_4\\
  \left(B_1 - \frac{B_4D_1}{D_4}\right)\dot{\Theta}_{bl} + \left(B_2 - \frac{B_4D_2}{D_4}\right)\dot{\Theta}_{ml} + \left(B_3 - \frac{B_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= X_1 - \frac{B_4}{D_4}X_4\\
  \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_1 - \frac{C_4D_1}{D_4}\right)\dot{\Theta}_{bl} + 
  \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\dot{\Theta}_{ml} + 
  \left(A_3 - \frac{A_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(X_1 - \frac{C_4}{D_4}X_4\right)\\
  D_1\dot{\Theta}_{bl} + D_2 \dot{\Theta}_{ml} + D_3 \dot{\Theta}_{mr} + D_4 \dot{\Theta}_{br} &= X_4 \\
\end{align}

\begin{align}
  \left(A_1 - \frac{A_4D_1}{D_4}\right)\dot{\Theta}_{bl} + \left(A_2 - \frac{A_4D_2}{D_4}\right)\dot{\Theta}_{ml} + \left(A_3 - \frac{A_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= X_1 - \frac{A_4}{D_4}X_4\\
  \left(B_1 - \frac{B_4D_1}{D_4}\right)\dot{\Theta}_{bl} + \left(B_2 - \frac{B_4D_2}{D_4}\right)\dot{\Theta}_{ml} + \left(B_3 - \frac{B_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= X_1 - \frac{B_4}{D_4}X_4\\
  \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_1 - \frac{C_4D_1}{D_4}\right)\dot{\Theta}_{bl} + 
  \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\dot{\Theta}_{ml} + 
  \left(A_3 - \frac{A_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(X_1 - \frac{C_4}{D_4}X_4\right)\\
  D_1\dot{\Theta}_{bl} + D_2 \dot{\Theta}_{ml} + D_3 \dot{\Theta}_{mr} + D_4 \dot{\Theta}_{br} &= X_4 \\
\end{align}

>>>>

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{fullpage}

@@

\section{Making solvable system of equations}

@@

\section{Breaking terms down into symbols}

@@

\section{System solution!}
This system is solved via Mathematica...\\
\begin{multline}
N_{bl} =
(-B_2 C_4 D_3 X_1 + B_2 C_3 D_4 X_1 + A_4 C_3 D_2 X_2 - A_3 C_4 D_2 X_2 - A_4 C_2 D_3 X_2 + A_2 C_4 D_3 X_2 +\\
 A_3 C_2 D_4 X_2 - A_2 C_3 D_4 X_2 + A_4 B_2 D_3 X_3 - A_3 B_2 D_4 X_3 - A_4 B_2 C_3 X_4 + A_3 B_2 C_4 X_4 +\\
B_4 (-C_3 D_2 X_1 + C_2 D_3 X_1 + A_3 D_2 X_3 - A_2 D_3 X_3 - A_3 C_2 X_4 + A_2 C_3 X_4) + B_3 (C_4 D_2 X_1 - \\
C_2 D_4 X_1 - A_4 D_2 X_3 + A_2 D_4 X_3 + A_4 C_2 X_4 - A_2 C_4 X_4)) \\
\end{multline}

\begin{multline}
N_{ml} =
(B_1 C_4 D_3 X_1 - B_1 C_3 D_4 X_1 - A_4 C_3 D1 X_2 + A_3 C_4 D1 X_2 + A_4 C_1 D_3 X_2 - A_1 C_4 D_3 X_2 - \\
A_3 C_1 D_4 X_2 + A_1 C_3 D_4 X_2 - A_4 B_1 D_3 X_3 + A_3 B_1 D_4 X_3 + A_4 B_1 C_3 X_4 - A_3 B_1 C_4 X_4 +\\
B_4 (C_3 D1 X_1 - C_1 D_3 X_1 - A_3 D1 X_3 + A_1 D_3 X_3 + A_3 C_1 X_4 - A_1 C_3 X_4) + B_3 (-C_4 D1 X_1 + \\
C_1 D_4 X_1 + A_4 D1 X_3 - A_1 D_4 X_3 - A_4 C_1 X_4 + A_1 C_4 X_4)) \\
\end{multline}

\begin{multline}
N_{mr} =
(-B_1 C_4 D_2 X_1 + B_1 C_2 D_4 X_1 + A_4 C_2 D1 X_2 - A_2 C_4 D1 X_2 - A_4 C_1 D_2 X_2 + A_1 C_4 D_2 X_2 + \\
A_2 C_1 D_4 X_2 - A_1 C_2 D_4 X_2 + A_4 B_1 D_2 X_3 - A_2 B_1 D_4 X_3 - A_4 B_1 C_2 X_4 + A_2 B_1 C_4 X_4 +\\
B_4 (-C_2 D1 X_1 + C_1 D_2 X_1 + A_2 D1 X_3 - A_1 D_2 X_3 - A_2 C_1 X_4 + A_1 C_2 X_4) + \\
B_2 (C_4 D1 X_1 - C_1 D_4 X_1 - A_4 D1 X_3 + A_1 D_4 X_3 + A_4 C_1 X_4 - A_1 C_4 X_4)) \\
\end{multline}

\begin{multline}
N_{br} =
(B_1 C_3 D_2 X_1 - B_1 C_2 D_3 X_1 - A_3 C_2 D1 X_2 + A_2 C_3 D1 X_2 + A_3 C_1 D_2 X_2 - A_1 C_3 D_2 X_2 - \\
A_2 C_1 D_3 X_2 + A_1 C_2 D_3 X_2 - A_3 B_1 D_2 X_3 + A_2 B_1 D_3 X_3 + A_3 B_1 C_2 X_4 - A_2 B_1 C_3 X_4 +\\
B_3 (C_2 D1 X_1 - C_1 D_2 X_1 - A_2 D1 X_3 + A_1 D_2 X_3 + A_2 C_1 X_4 - A_1 C_2 X_4) + \\
B_2 (-C_3 D1 X_1 + C_1 D_3 X_1 + A_3 D1 X_3 - A_1 D_3 X_3 - A_3 C_1 X_4 + A_1 C_3 X_4)) \\
\end{multline}

\begin{multline}
D = (A_2 B_4 C_3 D1 - A_2 B_3 C_4 D1 - A_1 B_4 C_3 D_2 + A_1 B_3 C_4 D_2 - A_2 B_4 C_1 D_3 + A_1 B_4 C_2 D_3 + \\
A_2 B_1 C_4 D_3 - A_1 B_2 C_4 D_3 + A_4 (B_3 C_2 D1 - B_2 C_3 D1 - B_3 C_1 D_2 + B_1 C_3 D_2 + B_2 C_1 D_3 - B_1 C_2 D_3) + \\
A_2 B_3 C_1 D_4 - A_1 B_3 C_2 D_4 - A_2 B_1 C_3 D_4 + A_1 B_2 C_3 D_4 + A_3 (-B_4 C_2 D1 + B_2 C_4 D1 + B_4 C_1 D_2 - B_1 C_4 D_2 - B_2 C_1 D_4 + B_1 C_2 D_4))
\end{multline}

\begin{align}
\dot{\Theta}_{bl} &= \frac{N_{bl}}{D} \\
\dot{\Theta}_{ml} &= \frac{N_{ml}}{D} \\
\dot{\Theta}_{mr} &= \frac{N_{mr}}{D} \\
\dot{\Theta}_{br} &= \frac{N_{br}}{D}
\end{align}
